[![Build Status](https://travis-ci.org/mpadge/rdeps.svg?branch=master)](https://travis-ci.org/mpadge/rdeps)
[![Build status](https://ci.appveyor.com/api/projects/status/github/mpadge/rdeps?svg=true)](https://ci.appveyor.com/project/mpadge/rdeps)
[![Project Status: Active](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![codecov](https://codecov.io/gh/mpadge/rdeps/branch/master/graph/badge.svg)](https://codecov.io/gh/mpadge/rdeps)

Automatically obtain source code for all packages which depend on a given R
package, either by opening github sites in browser, or downloading .tar.gz
files.

## Installation

```{r, eval=FALSE}
devtools::install_github ('mpadge/rdeps')
```
```{r, echo=FALSE, message=FALSE}
devtools::load_all ('.', export_all=FALSE)
#devtools::document ('.')
#devtools::check ('.')
#devtools::build_vignettes ()
#testthat::test_package ('.')
```

---------------

## Usage

```{r}
get_rdeps ('httr')
```

For those dependencies which have associated URLs, these can be automatically
opened with

```{r, eval=FALSE}
get_rdeps ('httr', fmt='url')
```

or the `.tar.gz` files of all packages which depend on the nominated pakcage can
be automatically downloaded with

```{r, eval=FALSE}
get_rdeps ('httr', fmt='tar')
```

